The Splashback Radius of Planck-SZ clusters

### 2019-02-14 Paper_v2/Reply_to_referee.txt

Reply: We thank the referee for a careful reading of the manuscript and the
detailed suggestions which have helped improve the paper.

>
>
> 1) The main points of the paper are somewhat hidden in a wealth of 16 figures
> and 6 tables, some of which seem detail-oriented and make the paper harder to
> digest than it needs to be. The suggestions below would drastically reduce the
> number of figures, without losing any essential information.
>
> a) Figure 1: It is not clear why the sky maps of the selected clusters are
> buried in the appendix while the mass-redshift distribution is shown in Figure
> 1. Both figures are relatively technical. My recommendation would be to shift
> Figure 1 into Appendix A, which could be renamed from "Sky maps" to "Properties
> of the SZ sample" or something like that.

Reply: Our original motivation to keep Figure 1 in the beginning was to show
the average redshift of the sample and the mass range, since that goes in our
theoretical expectation. However since this is indicated in Table 1, we have
now moved Figure 1 to the appendix based on the referee's suggestion. We have
renamed the appendix to "Properties of the SZ clusters and the PS galaxy
sample".

@@

>
> 2) Throughout the paper, I found that the writing supposed the reader to
> possess a high level of knowledge about the specifics of the splashback radius
> and its detection. It would be good to add some gentle explanations as well as
> smoother transitions between different sections and arguments. I give some
> examples below.
>
> a) In the abstract, an introductory sentence would help. What has been done so
> far, why move from optical to SZ selection? A comment to this effect would also
> be good in Section 2.1, some readers are probably confused as to the purpose of
> the SZ sample (which is used only to find clusters but not to constrain their
> profiles).

Reply: We have now included sentences to this effect in the abstract, the
introduction as well as just before Section 2.1.

>
> b) Throughout the paper, it is implicitly assumed that the definition of the
> splashback radius is the radius where the 3D slope of density is steepest, but
> that is only one of many definitions. It was defined this way in More+15 as the
> most easily measurable quantity, but one can also use the radius of the
> outermost shell in theoretical models (Adhikari+14, Shi 16), non-spherical
> shells (Mansfield+17), or the apocenter radii of particles (Diemer 17). To be
> clear, this comment is not intended as a sneaky citation request. I do,
> however, feel that there is already a lot of confusion as to "what the
> splashback radius actually is", and any splashback paper should try to
> alleviate this confusion.

Reply: We would like to apologize for missing these citations. We have now
pointed out these alternative ways of defining the splashback radius in the
Methods section, along with the relevant citations. We have also highlighted
the common thread connecting these different definitions, and mentioned the
reason we adopt a particular definition in the paper.

@@

>
> c) It is assumed that the reader understands the connection between the
> limiting magnitude of galaxy samples and dynamical friction, but that
> connection is far from obvious! Please explain that dynamical friction can
> reduce Rsp, that this effect is mass-dependent, and that selecting more massive
> galaxy samples can thus put limits on the effect. In this context, it would
> also be good to cite Adhikari+16 who measure and model the magnitude of
> dynamical friction in SDSS.

Reply: We have now added comments relevant to dynamical friction effects in the
introduction itself.

@@

Reply: We have now added a note discussing our results with those in Baxter et
al. 2017.

> a) The right panel of Figure 4 seems puzzling, should these slopes not be much
> steeper? Compare to Figure 4 in Baxter+17.

Reply: This was an erroneous plot, we apologize for not noticing this before,
and thank the referee for noticing it.

>
> b) In Section 4, you explain that the splashback radius seen in the blue
> population may be due to contamination of the blue sample, but the conclusion
> remains a little unclear in the main text. I would refer to Baxter+17 Figure 5,
> saying that they found no splashback in the blue population, and make a firm
> statement on whether there is any evidence that this is wrong (given the issues
> with contamination).

Reply: We now refer to Baxter et al. 2017, explain the differences between our
results. We refrain from making a strong statement given that the analysis
methods are different and the difference between which galaxies we consider
blue compared to what Baxter et al. adopt in their paper.

> 4) I have some smaller comments and questions regarding the text and figures.
>
> a) In Table 2, it looks like "'" were used instead of "." in large numbers.

Reply: We have now corrected this.

@@

>
> b) The derivatives in figures 2, 3 etc look somewhat noisy, even though the
> profile measure is smooth as it is inferred from the profile fitting function.
> My expectation would be that the derivatives should look smooth too?

Reply: The noisy looking derivatives were a result of us avoiding the large
computational cost of storing the derivatives at a large number of radial
points at every MCMC step. We have now taken the computed points, and plotted
a spline instead and are displaying it in the Figure to avoid this noise in
the derivative figure.

@@

> c) Section 4.1 is the only sub-section of Section 4, and thus makes no sense. I
> would either remove the 4.1 section title or add more sub-sections.

Reply: Agreed, we have now changed this.

> d) In Section 4, you state that you are using an "average concentration-mass
> relation" to convert M500c to M200m. Which model of the concentration-mass
> relation was used?

Reply: We now mention the model of concentration-mass relation we use (Diemer
and Kravtsov 2015).

@@

>
> e) In Figures 4 and 5, y-labels are missing (even though they are fairly
> obvious). Moreover, it would be good to increase the size of the inset labels
> that state what each panel is showing.

Reply: We have added the y-labels and increased the size of the inset labels.

>
> f) Figure 8 looks like a low-resolution pixel graphic. Is there a reason not to
> show it as a vector graphic?

Reply: We had included a png file, and now we have changed it to a pdf.

### 2019-02-14 Paper_v2/RSP_paper_new.tex
more edits
finalizing edits

\begin{figure}
	\centering{
    \includegraphics[scale=0.75]{MAIN_color_results_with_spline_no_mc.pdf}}
\caption{We present the cross-correlations inferred for the color-separated
galaxy samples. The two-dimensional cross-correlations
of the red and blue galaxy populations as inferred by
cross-correlating the cluster sample with the color-separated
subsamples that were extracted from the PS 21.5 galaxy catalog are
shown in the top panel, whereas the associated derivative profiles
are shown in the second one. The vertical, shaded bands indicate the
locations of steepest slope of the two-dimensional cross-correlation signal
as inferred from the two subsamples, whereas the black, dashed lines
indicate the upper and lower bounds of the same feature but as
estimated from the full PS 21.5 galaxy catalog.
Panels three to five show the corresponding three-dimensional
cross-correlations, as well as the corresponding
splashback radii (indicated by the colored, vertical bands) and
their first and second order derivative profiles. The light-colored
curves show the corresponding first and second order derivatives of the one-halo
term (namely $\rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r)$ in Equation~\ref{eq:model}). Here, the black, dashed lines indicate upper and lower bounds of the
three-dimensional splashback radius corresponding to the full PS 21.5 galaxy sample.}
   \label{fig:color_curve_all}
\end{figure}

@@

We perform a preliminary comparison of the measurements with
expectations from cold dark matter models. The average halo mass of
the PSZ2 clusters as estimated from the Sunyaev-Zeldovich signal
is $M_{\rm 500c}=3.0\times10^{14}$ $\msunh$. We convert this mass
estimate to $M_{\rm 200m}=6.2\times10^{14}$ $\msunh$ using the average
concentration mass relation of halos assuming an NFW profile
\citep{HuKravtsov:2003}. Given the average mass and redshift of our
cluster sample, we calculate the expected splashback radius to be
$1.89$ $\mpch$. We base this estimate on the fitting functions
presented in \citet{more2015splashback}. The splashback radius we
find for the three samples is consistent with this expectation,
although we can not rule out $\sim 15\%$ deviations in either directions,
given our large error bars.

@@

\textbf{At face value, this result seems to be at odds with the findings
presented by \citet{baxter2017halo}, who find no splashback feature in the blue
galaxy population. Our independent investigations suggest that the splashback
feature gets less prominent as we cross-correlate the galaxy clusters with
galaxies which are progressively bluer in color. In their paper,
\citet{baxter2017halo} considered the bluest quartile of the galaxy population.
Therefore, it is conceivable that they see no evidence for the splashback
feature in their dataset in the bluest population of galaxies. We would also
like to note that the approach used by \citet{baxter2017halo} used to separate
galaxies into red and blue populations is also fundamentally different from our
approach. While \citet{baxter2017halo} use K-corrected magnitudes from SDSS
relying on the photometric redshifts of galaxies (which could have different
uncertainties for the red and the blue population), we rely on a color cut
which depends upon the redshift of the cluster under consideration.}

@@

\section*{Acknowledgements}
DZ is grateful to Kavli IPMU for its hospitality during this research
project. SM is supported by a grant-in-aid by the Japan Society for
Promotion of Science (JSPS), grant number 16H01089. We acknowledge
useful discussions regarding this work with Benedikt Diemer, Neal
Dalal, Bhuvnesh Jain, Andrey Kravtsov, as well as participants of the
KITP UCSB workshop on the Galaxy-Halo connection in 2017. SM was
supported in part by the National Science Foundation under Grant No.
NSF PHY-1125915 during this workshop. Further, we also thank the anonymous
referee for helpful comments and suggestions during the development of this 
manuscript.

@@

\section{Visualization of the Data}
\label{sec:figures}

We visualize some of the main properties of the used data catalogs.
In Fig.~\ref{fig:planck_summary} we show the mass and
the redshift distribution of the Planck clusters.
In Figure~\ref{fig:skymaps} we present the sky locations of the SZ selected clusters from the PSZ2 catalog that we used in our study (red points). The purple areas mark the masked out regions of the galaxy catalogs. All sky maps presented use the ICRS coordinate system.

>>>>

\begin{figure}
	\centering{
    \includegraphics[trim = 0mm 2mm 0mm 0mm, clip,scale=0.75]{MAIN_color_results_with_spline_no_mc_1.pdf}
    \includegraphics[trim = 0mm 2mm 0mm 0mm, clip,scale=0.75]{MAIN_color_results_with_spline_no_mc_2.pdf}}
\caption{We present the cross-correlations inferred for the color-separated
galaxy samples. The two-dimensional cross-correlations
of the red and blue galaxy populations as inferred by
cross-correlating the cluster sample with the color-separated
subsamples that were extracted from the PS 21.5 galaxy catalog are
shown in the top panel, whereas the associated derivative profiles
are shown in the second one. The vertical, shaded bands indicate the
locations of steepest slope of the two-dimensional cross-correlation signal
as inferred from the two subsamples, whereas the black, dashed lines
indicate the upper and lower bounds of the same feature but as
estimated from the full PS 21.5 galaxy catalog.
Panels three to five show the corresponding three-dimensional
cross-correlations, as well as the corresponding
splashback radii (indicated by the colored, vertical bands) and
their first and second order derivative profiles. The light-colored
curves show the corresponding first and second order derivatives of the one-halo
term (namely $\rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r)$ in Equation~\ref{eq:model}). Here, the black, dashed lines indicate upper and lower bounds of the
three-dimensional splashback radius corresponding to the full PS 21.5 galaxy sample.}
   \label{fig:color_curve_all}
\end{figure}

@@

We perform a preliminary comparison of the measurements with
expectations from cold dark matter models. The average halo mass of
the PSZ2 clusters as estimated from the Sunyaev-Zeldovich signal
is $M_{\rm 500c}=3.0\times10^{14}$ $\msunh$. We convert this mass
estimate to $M_{\rm 200m}=6.2\times10^{14}$ $\msunh$ using the average
concentration mass relation of halos \citep{Diemer2015} assuming an NFW profile
\citep{HuKravtsov:2003}. Given the average mass and redshift of our
cluster sample, we calculate the expected splashback radius to be
$1.89$ $\mpch$. We base this estimate on the fitting functions
presented in \citet{more2015splashback}. The splashback radius we
find for the three samples is consistent with this expectation,
although we can not rule out $\sim 15\%$ deviations in either directions,
given our large error bars.

@@

\textbf{At face value, this result seems to be at odds with the findings
presented by \citet{baxter2017halo}, who find no splashback feature in the blue
galaxy population. Our independent investigations suggest that the splashback
feature gets less prominent as we cross-correlate the galaxy clusters with
galaxies which are progressively bluer in color. In their paper,
\citet{baxter2017halo} considered the bluest quartile of the galaxy population.
Therefore, it is conceivable that they see no evidence for the splashback
feature in their dataset in the bluest population of galaxies. We would also
like to note that the approach used by \citet{baxter2017halo} used to separate
galaxies into red and blue populations is also fundamentally different from our
approach. While \citet{baxter2017halo} use K-corrected magnitudes from SDSS
relying on the photometric redshifts of galaxies (which could have different
uncertainties for the red and the blue population), we rely on a color cut
which depends upon the redshift of the cluster under consideration. The
differences in our conclusions therefore need to be carefully examined given
these analysis differences.}

@@

\section*{Acknowledgements}
DZ is grateful to Kavli IPMU for its hospitality during this research
project. SM is supported by a grant-in-aid by the Japan Society for
Promotion of Science (JSPS), grant number 16H01089. We acknowledge
useful discussions regarding this work with Benedikt Diemer, Neal
Dalal, Bhuvnesh Jain, Andrey Kravtsov, as well as participants of the
KITP UCSB workshop on the Galaxy-Halo connection in 2017. SM was
supported in part by the National Science Foundation under Grant No.
NSF PHY-1125915 during this workshop. Further, we also thank the anonymous
referee for helpful comments and suggestions which helped improve the
manuscript.

@@

\section{Properties of the SZ clusters and the PS galaxy sample}
\label{sec:figures}

We present the main properties of the data catalogs we have used in our
analysis. In Fig.~\ref{fig:planck_summary}, we show the mass and the redshift
distribution of the Planck SZ clusters. In Figure~\ref{fig:skymaps}, we present
the sky locations of the SZ selected clusters from the PSZ2 catalog that we
used in our study (red points). The purple areas mark the regions which have
been masked out from the galaxy catalogs. All sky maps presented use the ICRS
coordinate system.
